---
  output: html_document
---
  Elements Of Data Visualization Final Project: Cancer Data Analysis
===
  __By Alex Cortez, Adam Hernandez, and Alex Pearce__

__GitHub__: https://github.com/ACollectionOfAtoms/DV_FinalProject

This data was provided by the Enigma.io database. It is described as such:
United States Cancer Statistics (USCS) information is aggregated from thousands of local cancer registries and published by the National Program of Cancer Registries (NPCR), a division of the Centers for Disease Control and Prevention (CDC).

## Load necessary packages
```{r message=FALSE}
source("../01 Data/load_packages.R",echo=TRUE)
```

## Dataframe Creations
```{r message=FALSE}
source("../01 Data/cancer_tables.R",echo=TRUE)
```

***

## An analysis of cancer, age, death, and incidence through data wrangling. 
```{r message=FALSE}
source("../02 Data Wrangling/general_age_analysis.R",echo=TRUE)
```

## Inspecting Age and Site
```{r message=FALSE}
source("../02 Data Wrangling/age_site.R",echo=TRUE)
```

## Further analysis, introducing race. 
```{r message=FALSE}
source("../02 Data Wrangling/age_site2.R",echo=TRUE)
```